\bfseries\LARGE Vision Vs. LiDAR/Radar Fusion in Autonomous Driving Systems

### 2025-05-28 Papers/Paper One/TopicOne.tex
work on cleaning up

\subsubsection{Pulsed ToF:}
Pulsed TOF techniques are the simplest of the three cases in which distance is
determined by multiplying the speed of light in a medium by the time a light
pulse takes to travel the distance to the target:
\begin{equation}
R_{\text{pulse}} = \frac{c}{2} t_{\text{oF}},
\label{eq:tof_pulse}
\end{equation}
where $R_{oF}$ is the distance the light ray travels, $c$ is the speed of
light in free space, and $t_{oF}$ is the time it takes for the pulse of energy
to travel from its emitter to the observed object and then back to the receiver.
This high-power method provides centimeter accuracy. This method is shown in
Figure~\ref{fig:pulse}.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{lidar.png}
	\caption{The Pulsed Approach to Determining Object Distance \cite{2019Royo}}
	\label{fig:pulse}
\end{figure}

>>>>

\subsubsection{Pulsed ToF:}
Pulsed TOF techniques are the simplest of the three cases in which distance is
determined by multiplying the speed of light in a medium by the time a light
pulse takes to travel the distance to the target:
\begin{equation}
R = \frac{c}{2} t_{\text{oF}},
\label{eq:tof_pulse}
\end{equation}
where $R$ is the distance the light ray travels, $c$ is the speed of
light in free space, and $t_{oF}$ is the time it takes for the pulse of energy
to travel from its emitter to the observed object and then back to the receiver.
This high-power method provides centimeter accuracy \cite{2019Royo}. This method is shown in
Figure~\ref{fig:pulse}.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{lidar.png}
	\caption{The Pulsed Approach to Determining Object Distance \cite{2019Royo}}
	\label{fig:pulse}
\end{figure}
